Analysis of Cartesian Genetic Programming's Evolutionary Mechanisms

### 2013-07-16 CGP Journal/main.tex
Added a TODO so I would stop forgetting to do the acknowledgements
Manually filled in my citation information, wrote a bibliography

The authors would like to thank...

@@

\begin{IEEEbiography}{Brian W. Goldman}
TODO
\end{IEEEbiography}

>>>>

TODO
The authors would like to thank...

@@

\begin{IEEEbiography}{Brian W. Goldman}
received the B. S. degree and M.S. degree in computer science from the
Missouri University of Science and Technology, Rolla, in 2010
and 2012 respectively.

He is currently a Ph.D. student with the Department of Computer Science
and Engineering at Michigan State University, East Lansing.  His current
research interests include evolutionary computation and genetic programming.

\end{IEEEbiography}
